\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2018-08-07 paper/ms.tex
Use tag 0.2.3 (doesn't exist yet)

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
\pkg{numba} \citep{numba},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
%
\begin{CodeChunk}
\begin{CodeInput}
$ wget https://github.com/eggplantbren/DNest4/archive/0.1.4.tar.gz
$ tar xvzf 0.1.4.tar.gz
$ mv DNest4-0.1.4 DNest4
$ cd DNest4/code
$ make
$ cd ../python
$ python setup.py install
\end{CodeInput}
\end{CodeChunk}
%
In Mac OS X, the final line (which installs the \proglang{Python} parts
of \pkg{DNest4})
needs to provide information about
your OS version. For example, if your computer runs Mac OS X 10.9,
the installation command for the \proglang{Python} package is:
%
\begin{CodeChunk}
\begin{CodeInput}
$ MACOSX_DEPLOYMENT_TARGET=10.9 python setup.py install
\end{CodeInput}
\end{CodeChunk}
%
We recommend to create an environment variable called \code{DNEST4\_PATH}
and set it to the directory {\em above} the \pkg{DNest4} directory. Then,
if the model templates from the \pkg{DNest4} repository are copied
to any other location on your system and used as the basis for
new work, their Makefiles will continue to function.

>>>>

The \proglang{Python}
packages \pkg{NumPy} \citep{numpy}, \pkg{matplotlib} \citep{matplotlib},
\pkg{Numba} \citep{numba},
and \pkg{Cython} \citep{cython} are also needed.
To download and compile \pkg{DNest4}
the following steps are sufficient:
%
\begin{CodeChunk}
\begin{CodeInput}
$ wget https://github.com/eggplantbren/DNest4/archive/0.2.3.tar.gz
$ tar xvzf 0.2.3.tar.gz
$ mv DNest4-0.2.3 DNest4
$ cd DNest4/code
$ make
$ cd ../python
$ python setup.py install
\end{CodeInput}
\end{CodeChunk}
%
In Mac OS X, the final line (which installs the \proglang{Python} parts
of \pkg{DNest4})
needs to provide information about
your OS version. For example, if your computer runs Mac OS X 10.9,
the installation command for the \proglang{Python} package is:
%
\begin{CodeChunk}
\begin{CodeInput}
$ MACOSX_DEPLOYMENT_TARGET=10.9 python setup.py install
\end{CodeInput}
\end{CodeChunk}
%
We recommend to create an environment variable called \code{DNEST4\_PATH}
and set it to the directory {\em above} the \pkg{DNest4} directory. Then,
if the model templates from the \pkg{DNest4} repository are copied
to any other location on your system and used as the basis for
new work, their Makefiles will continue to function.
